\thetitle

### 2021-05-26 writing/discussion.tex
9.2 weakened

The validity of these conclusions is threatened in two distinct
ways. The first set of threats concerns easy-to-tune parameters of the
experiment and have been mentioned before: (i) the
representativeness of benchmarks; (ii) the relation between the mutations and real
programming mistakes; and (iii) the sampling strategy.  While the experimental setup attempts to
mitigate against these threats, the reader must definitely take into account
these limitations of the experiment when generalizing its conclusions.

The second set of threats connects the fundamental ideas and infrastructure of the experiment with reality or, more
precisely, assess how close the connection is. To start with, it questions the
realism of the rational programmer itself (sec.~\ref{sub:rational}), followed by
the definition of ``interesting scenarios''
(sec.~\ref{sec:threat:erasure-bias}).  The remaining questions address the
accuracy and the cost of Transient blame, respectively (see
secs.~\ref{sec:threat:transient} and~\ref{sec:threat:transient2}).

>>>>

The validity of these conclusions is threatened in two distinct ways. The first
set of threats concerns aspects of the experimental setup discussed in preceding
sections: (i) the representativity of benchmarks; (ii) the relation between the
mutations and real programming mistakes; and (iii) the sampling strategy.
Although the experimental setup attempts to mitigate against these threats, the
reader must definitely keep these limitations in mind when drawing conclusions.

The second set of threats questions four rather different aspects. To start
with, the realism of the rational programmer itself is questionable
(sec.~\ref{sub:rational}) as is the definition of ``interesting scenarios''
(sec.~\ref{sec:threat:erasure-bias}).  The remaining threats are about the
accuracy and cost of Transient blame, respectively
(secs.~\ref{sec:threat:transient} and~\ref{sec:threat:transient2}).
